\documentclass[letterpaper,12pt,final]{letter}
\usepackage[left=1.25in,right=1.25in,top=1.5in,bottom=1.5in]{geometry}
\longindentation=0pt
\usepackage{ebgaramond}
\usepackage{helvet}
\usepackage{microtype}
\usepackage{draftwatermark}
\SetWatermarkScale{1.2}
\SetWatermarkText{\textsf{\textbf{DRAFT}}}

\address{
  112 West Avenue\\
  Apt. 239\\
  San Marcos, TX 78666
}

\begin{document}
\begin{letter}{
  Ms. Susan Tilka, Lecturer\\
  Department of English\\
  Texas State University\\
  San Marcos, TX 78666
}

\opening{Dear Ms. Tilka:}

%% Introductory paragraph
I would like to introduce myself.
I am a research assistant in the Computer Science department at Texas State University.
I am a senior in the undergraduate program and I am double-majoring in Computer Science and Mathematics.
I plan to receive my degree at the end of the Spring 2015 semester.

%% Weaknesses
I have developed several bad habits in my writing.
My writing tends to suffer from wordiness; I spend much of the writing process simplifying my language as a result.
I tend to use dated vocabulary and an overly formal tone.
I often find myself contorting sentences to avoid ending a clause with a preposition.
I rarely let consecutive related statements stand apart; I prefer to connect them with conjunctions or semicolons.
I feel that this style flows better, but it is probably less clear.

%% Paragraph on paper
I have some writing experience in the professional world.
I recently co-authored a peer-reviewed paper with one of my research colleagues.
This paper was accepted this summer for publishing by the ACM and by the Academy of Science and Engineering.
As the primary author of the paper, I composed the majority of its content.
The structure and style of my writing received strong positive feedback from the reviewers.

%% Professional goals
Professionally, I am leaning toward a career in systems programming.
In addition to day-to-day communications, there is one very important application of technical communication skills in this field: documentation.
Documentation may refer to the reference materials used by the consumer of a program.
It may also refer to the internal annotations used by developers to convey important information about the design and implementation of a program.
Low-quality documentation is a persistent problem in my field, and I expect the skills I learn in this course to be helpful in addressing that problem.

%% Research
I have considered a career in research.
Whether I were to research in academia or in the private sector, technical communication skills would be of vital importance.
I have learned firsthand that effective research requires a high volume and high quality of technical communication.
As in software development, research requires a lot of documentation.
In addition to internal and end-user documentation, research requires documentation of process.
Without high-quality technical records of research processes, experiments can be difficult to reproduce---if they pass the peer review process at all.

%% Closing paragraph
I hope to come out of this class a better writer with a firmer foundation in technical communication.
I expect these skills to be very useful both as I continue my undergraduate research at Texas State and when I enter the field as a professional.
I look forward to your feedback and a productive semester.

\signature{
  Stuart Olsen
}
\closing{Sincerely,}

\end{letter}
\end{document}