\documentclass[12pt]{article}
\usepackage{fullpage}

\title{Abstract -- ``A Comparison of Programming Languages in Economics''}
\author{Stuart Olsen}

\begin{document}
\maketitle

\section*{Abstract}
In ``A Comparison of Programming Languages in Economics,''\cite{NBERw20263} published by the National Bureau of Economic Research, Aruoba et al.\ compare the speed of several programming languages. The purpose of the comparison is to provide a basis for assessing the benefits of various programming languages for use in numerical computation. The researchers accomplish this by reporting the speed of these languages under controlled conditions. The target audience is young economists and researchers who are new to using computers for numerical computations.

The researchers implement the same algorithm in each language and do not use language-specific features; the researchers impose these constraints to ensure that the results reflect the properties of each language, rather than the researchers' familiarity with each language. The researchers choose the algorithm they use to perform the comparison to be representative of typical numerical computations. The researchers run their tests using the most popular operating environments for the target audience.

The researchers present the execution times of their implementations as the primary experimental results of the paper. The researchers directly relate these raw results to the speed of each language. The researchers explicitly do not compare the difficulty of implementation in each language or any other parameters which might be used to assess the benefits of choosing a language for numerical computation; speed is the sole parameter of focus.

\section*{Search Terms}

\bibliographystyle{acm}
\bibliography{5.bib}

\end{document}